CRUSE to Safe Cycling in Ireland \\\large{An Open Source Methodology to Support Active Travel}

### 2023-09-13 cruse-paper.qmd
Add website stuff, close #1

# Uncomment for draft versions:
format: 
  docx: default
  html:
    output-file: index.html
  pdf:
    output-file: cruse-paper.pdf 
  gfm:
    output-file: README.md
number-sections: true

>>>>

# # Uncomment for draft versions:
# format: 
#   docx: default
#   html:
#     output-file: index.html
#   pdf:
#     output-file: cruse-paper.pdf 
#   gfm:
#     output-file: README.md
# number-sections: true

### 2023-09-13 cruse-paper.tex
Add website stuff, close #1

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, boxrule=0pt, breakable]}{\end{tcolorbox}}\fi

\hypertarget{th-transport-research-arena-tra-2024-dublin-ireland}{%
\subsection*{10th Transport Research Arena, TRA 2024, Dublin,
Ireland}\label{th-transport-research-arena-tra-2024-dublin-ireland}}
\addcontentsline{toc}{subsection}{10th Transport Research Arena, TRA
2024, Dublin, Ireland}

@@

\citep{lovelace2017}

• Title page/main information (title, full names and institutional
addresses for all authors, indication of the corresponding author) •
Abstract • Introduction • Results • Discussion (can be combined in
`Results and Discussion' section) • Conclusions • Methods/Experimental
(can also be placed after Introduction) • List of abbreviations •
Declarations\emph{ o Availability of data and material o Funding o
Acknowledgements o Competing interests o Authors' contributions o
Authors' information (optional) o }If any of the sections are not relev

  \bibliography{bibliography.bib}

>>>>

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, frame hidden, interior hidden, breakable, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

Transport is a major contributor to climate change, premature death due
to road traffic collisions and air pollution, yet has the potential to
be a major contributor to decarbonization and improved public health.
Transport is responsible for 23\% of global emissions, 70\% of which is
from road transport, nearly half of which is from passenger cars
\citep{jaramillo2022}. The transport system encourages, enables and in
some cases enforces unsustainable lifestyles, including over-consumption
of goods due to excessive mobile storage space and dependency on
services that are only accessible by car due to land use plans that have
built up around roads \citep{gray2001, shergold2012, motte-baumvol2010}.

Recognizing the impacts of poorly designed and performing transport
systems on their citizens, governments in many countries have set
targets and taken actions and set targets. In the context of climate,
road safety and physicial inactivity crises, policies to improve
transport systems can be classified according to the
\textquotesingle Avoid-Shift-Improve\textquotesingle{} (ASI) framework
\citep{jaramillo2022}. The framework highlights the importance of demand
reduction (\emph{avoid}ing unnecessary trips), in addition to mode
\emph{shift} and \emph{improvement} of existing energy converters, in
that order.

Uptake of cycling, the main topic of this paper, should be seen in this
broader context of transport decarbonisation. Although cycling uptake
appears on the surface to only relate to the `shift' part of the ASI
framework, closer consideration of the knock-on impacts of cycling
uptake shows that it can also help avoid unnecessary trips {[}citation
needed, any ideas Hussein?{]} . The rapid uptake of highly efficient
e-bikes can also be seen as an improvement on most electric vehicles,
which are too heavy and expensive to be a sustainable alternative and
could in fact delay the transition away from car dependency {[}citation
needed{]}.

At the European Union level \ldots{}

In Ireland\ldots{}

{[}Gary, Suzanne, others input here please.{]}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

Commute and school travel

Other trip purposes

{[}Joey please add your bit here.{]}

Bit on Jittering \citep{lovelace2022}

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

\hypertarget{list-of-abbreviations}{%
\section{List of abbreviations}\label{list-of-abbreviations}}

\hypertarget{declarations}{%
\section{Declarations}\label{declarations}}

\hypertarget{availability-of-data-and-material}{%
\subsection*{Availability of data and
material}\label{availability-of-data-and-material}}
\addcontentsline{toc}{subsection}{Availability of data and material}

\hypertarget{funding}{%
\subsection*{Funding}\label{funding}}
\addcontentsline{toc}{subsection}{Funding}

\hypertarget{acknowledgements}{%
\subsection*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{subsection}{Acknowledgements}

\hypertarget{competing-interests}{%
\subsection*{Competing interests}\label{competing-interests}}
\addcontentsline{toc}{subsection}{Competing interests}

\hypertarget{authors-contributions}{%
\subsection*{Authors' contributions}\label{authors-contributions}}
\addcontentsline{toc}{subsection}{Authors' contributions}

\renewcommand\refname{References}
  \bibliography{bibliography.bib}
